Sparse Function-space Representation \\ of Neural Networks

### 2023-05-17 paper/main.tex
Add UCI table to appendix (to be polished)
Minor

\section{Experiments}
\label{sec:experiments}
%
We present a series of experiments designed to demonstrate the versatility and efficacy of our proposed \our framework. We seek to find answers to the following questions: 
\textbf{Predictions:}~Does our method's ability to consider the full data set offer benefits over subset function-space methods? (\cref{sec:uci}) How do predictions with our sparse function-space approximation compare to weight-space approximations? 
\textbf{Function-space updates:} How fast are our function-space updates relative to retraining from scratch? Do they improve predictive performance? Are they as good as retraining from scratch? \todo{what do we have on this?}
\textbf{Representation:} Can a sparse function-space representation help retain knowlegde from previous tasks in CL? (\cref{sec:cl-exp})
\textbf{Uncertainty:} Can our uncertainty estimates help exploration in RL under sparse rewards? (\cref{sec:rl-exp})

@@

\paragraph{Toy examples} \cref{fig:teaser} and \cref{fig:banana}

>>>>

\section{Experiments}
\label{sec:experiments}
%
We present a series of experiments designed to demonstrate the versatility and efficacy of our proposed \our framework. We seek to find answers to the following questions: 
\textbf{Predictions:}~Does our method's ability to consider the full data set offer benefits over subset function-space methods? (\cref{sec:uci,sec:image}) How do predictions with our sparse function-space approximation compare to weight-space approximations? 
%\textbf{Function-space updates:} How fast are our function-space updates relative to retraining from scratch? Do they improve predictive performance? Are they as good as retraining from scratch? \todo{what do we have on this?}
\textbf{Representation:} Can a sparse function-space representation help retain knowlegde from previous tasks in CL? (\cref{sec:cl-exp})
\textbf{Uncertainty:} Can our uncertainty estimates help exploration in RL under sparse rewards? (\cref{sec:rl-exp})

@@

\paragraph{Toy examples} For illustrative purposes, we smoke-test our approach on a 1D regression problem (\cref{fig:teaser}) and on the 2D Banana classification task (\cref{fig:banana}). In \cref{fig:teaser}, we train an MLP neural network with two hidden layers (64 hidden units each, tanh activation). The middle panel shows the \our result on a sparse set of data examples, while the rightmost panel demonstrates fast dual conditioning on new data (from \cref{sec:sequential}). In \cref{fig:banana}, we use an MLP with two hidden layers (64 units, sigmoid) and compare to the HMC result obtained by hamiltorch \cite{cobb:} (10~chains, 10,000 samples).
